Induced universal graphs for families of small graphs

### 2021-08-31 paper/paper.tex
Delete an extra word
Fix grammar

The full set of experiments described in this paper, run sequentially, required
took less than an hour complete on a laptop with an Intel Core i5-6200U CPU
and 8 GB RAM.\footnote{The code and
results from this paper, including lists of minimal induced universal graphs
in graph6 format, are available from
\url{https://github.com/jamestrimble/small-universal-graphs}}

@@

    We will show that $G$ cannot contain as induced subgraphs both
    one of the graphs in Figure~\ref{fig:boundproof}.  These graphs are complements
    of each other, and we refer to them as $H$ and $H'$ respectively.

>>>>

The full set of experiments described in this paper, run sequentially,
took less than an hour to complete on a laptop with an Intel Core i5-6200U CPU
and 8 GB RAM.\footnote{The code and
results from this paper, including lists of minimal induced universal graphs
in graph6 format, are available from
\url{https://github.com/jamestrimble/small-universal-graphs}}

@@

    We will show that $G$ cannot contain as induced subgraphs both
    of the graphs in Figure~\ref{fig:boundproof}.  These graphs are complements
    of each other, and we refer to them as $H$ and $H'$ respectively.
